\documentclass[letterpaper,11pt]{article}

\setlength{\footskip}{5pt}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\setlength{\footskip}{5pt}
\usepackage[english]{babel}
\usepackage{tabularx}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Zachary Ellison} \\ \vspace{1pt}
    \small $|$ \href{https://zacharyellison.net}{\underline{zacharyellison.net}} $|$ 
    \href{https://linkedin.com/in/zachary-ellison}{\underline{LinkedIn}} $|$
    \href{https://github.com/zacharyellison}{\underline{Github}} $|$
    \href{https://calendly.com/zach-r-ellison/intro-call}{\underline{Calendly}} $|$ \\
    $|$ \href{mailto:zach.r.ellison@gmail.com}{\underline{zach.r.ellison@gmail.com}} $|$ 
    720-333-0012 $|$
    {Boston MA, 02135} $|$
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harvard University}{Class of 2020}
      {Bachelor of Arts in Computer Science}{Cambridge, MA}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Backend Engineer}{September 2024 -- Present}
      {Ribbiot}{Remote}
      \resumeItemListStart
        \resumeItem{Architected backend services, APIs, and data models for an industrial operations platform, supporting scalable workflows for enterprise clients.}
        \resumeItem{Optimized CI/CD pipelines in collaboration with DevOps, reducing deployment failures by 35\% and speeding delivery cycles.}
        \resumeItem{Designed modular job and task management workflows, enabling rapid client-specific customization without code changes.}
        \resumeItem{\textbf{Tech}: AWS, Serverless, Typescript, GraphQL, GitHub Actions, CircleCI, DataDog, SQL, Docker}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{September 2022 -- September 2024}
      {Notable}{Remote}
      \resumeItemListStart
        \resumeItem{Automated healthcare administration tasks using Python computer vision, reducing manual processing by 60\%.}
        \resumeItem{Led a team of 5 contractors, improving iteration speed and task reliability across automation projects.}
        \resumeItem{Directed decisions on code quality and architectural patterns, resulting in 40\% fewer review corrections.}
        \resumeItem{Built integrations for web payor portals using Python, Typescript, and GCP, ensuring HIPAA-compliant data ingestion.}
        \resumeItem{\textbf{Tech}: GCP, Typescript, Selenium, Python, Jenkins, Concourse, SQL, Docker, Jest}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{January 2022 -- August 2022}
      {Zagaran Inc}{Boston, MA}
      \resumeItemListStart
        \resumeItem{Refactored Django codebase, improving scalability and maintainability across multiple applications.}
        \resumeItem{Optimized database ingestion and querying, achieving 3x performance improvement.}
        \resumeItem{\textbf{Tech}: Django, Python3, Numpy, Postgres, Pandas, Angular, React, Node.js, AWS}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer in Test}{March 2021 -- January 2022}
      {EzeSoft, SS\&C}{Remote / Boston, MA}
      \resumeItemListStart
        \resumeItem{Developed a Kubernetes-based performance testing framework, providing actionable insights to stakeholders.}
        \resumeItem{Introduced a data architecture framework to support test-driven development, improving test coverage by 50\%.}
        \resumeItem{Owned integration and unit test development across services, ensuring higher code reliability.}
        \resumeItem{\textbf{Tech}: C\#, Node.js, Jest, Jenkins, Jira, Kubernetes, C++, Tableau, AWS}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist}{September 2018 -- September 2019}
      {Activision}{Boulder, CO}
      \resumeItemListStart
        \resumeItem{Performed sentiment analysis on 600k+ users, informing product decisions and marketing strategies.}
        \resumeItem{Built ETL pipelines processing 18M+ posts with Python, Kafka, and AWS, reducing data latency by 70\%.}
        \resumeItem{Developed internal analytics tools using React and Flask, improving data exploration efficiency.}
        \resumeItem{Implemented multithreaded workers using Celery and Redis to process high-volume datasets reliably.}
        \resumeItem{\textbf{Tech}: Python, Kafka, React, Celery, Redis, Spark, Kubernetes, Docker, AWS, MongoDB, SQL, Snowflake}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Typescript, Python, C/C++, Java, SQL, JavaScript, Node.js, React, Bash} \\
     \textbf{Databases}{: Postgres, MSSQL, MySQL, Redshift, MongoDB, Elasticsearch} \\
     \textbf{Architecture}{: Microservices, Serverless systems, Event-driven Workflows, CRUD APIs} \\
     \textbf{Libraries}{: Flask, Django, Prisma ORM, Jest, PyTest, GraphQL, Selenium, Pandas, NumPy, scipy} \\
     \textbf{Developer Tools}{: Git, Docker, CircleCI, Kubernetes, AWS, GCP, S3, IAM, Jenkins, claude code, opencode, roo, cline, QWEN, Codex} \\
     \textbf{Interests}{: Backend systems design, cloud architecture, data engineering, AR/VR hobby projects, lifting, running, and yoga, sourdough baking}
    }}
 \end{itemize}

\end{document}
